---
title: "Unit 1 - 3 Review Starter"
author: "Group 3"
date: "October 4th, 2021"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sand_minerals <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sand_minerals)
names(sand_minerals)
```
There are `r nrow(sand_minerals)` rows and there are `r ncol(sand_minerals)` variables.
The first row represents the location of where the mineral was found. The second row represents the type of mineral collected.

### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
glimpse(solubility_hardness)
glimpse(location_descriptions)
names(density)
names(solubility_hardness)
names(location_descriptions)
```
There are `r nrow(density)` and `r ncol(density)` rows and columns for density
There are `r nrow(solubility_hardness)` and `r ncol(solubility_hardness)`rows and columns for solubility hardness respectively.
There are `r nrow(location_descriptions)` and `r ncol(location_descriptions)` rows and columns for location descriptions respectively.

for density and solubility_hardness, each row is a different mineral: Biotite, Feldspar, and Quartz. For location_descriptions, each row is a numerical value of 1-10, paired with a character description of what the location is defined as.

### Exercise 3

```{r join-mineral-properties}
 sand_mineral_density <- sand_minerals %>% 
  full_join(density)
solubility_hardness %>%
  full_join(sand_mineral_density)
 
```
The output has `r nrow(sand_mineral_density)` rows.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
